\Large \bf Rethinking Service Systems: \\ A Path Towards Secure and Equitable Resource Markets

### 2020-06-08 CESC-submission/paper.tex
add figure for PCD solution

For the \emph{ZKP-based} solution, in the NuCypher network, each Ursula produces a zero knowledge proof attesting to the correctness of the re-encryption she performed to be checked by Bob~\cite{umbral2018}. We can combine the proofs of all served requests within a round into one attesting to the following statement: \emph{``An Ursula has served $\omega$ distinct requests correctly"} for some positive integer $\omega$ representing the number of served requests. This accumulation can be done by using generic techniques like proof carrying data (PCD)~\cite{chiesa2010proof} or incrementally verifiable computation (IVC)~\cite{valiant08}.

>>>>

For the \emph{ZKP-based} solution, in the NuCypher network, each Ursula produces a zero knowledge proof attesting to the correctness of the re-encryption she performed to be checked by Bob~\cite{umbral2018}. We can combine the proofs of all served requests within a round into one attesting to the following statement: \emph{``An Ursula has served $\omega$ distinct requests correctly"} for some positive integer $\omega$ representing the number of served requests. This accumulation can be done by using generic techniques like proof carrying data (PCD)~\cite{chiesa2010proof} or incrementally verifiable computation (IVC)~\cite{valiant08}. Figure~\ref{pcd-based-sol} for a high level diagram describing this solution (here $x_i$ is the $i^{th}$ request coming from Bob, $cFarg_i$ is the fragment of the transformed ciphertext (the reply for the re-encryption service request), $\pi_i$ is the correctness proof for handling this request, and $\hat{\pi}_i$ is the aggregated proof covering all proofs for requests $1, \dots, i$.

\begin{figure}[t!]
\centerline{
\includegraphics[height= 0.7in, width = 1.0\columnwidth]{figures/pcd-based-sol.pdf}}
\caption{PCD/IVC-based solution diagram. Ursula starts a round in the idle state. When 
the first request arrives, Ursula responds to the request and starts composing the 
proofs as new requests arrive. At the end of the round, Ursula announces the number of 
served requests and a single proof attesting to its claim to the network. }
\label{pcd-based-sol}
\end{figure}
